---
title: "Music insights project, part 2"
output:
  html_document:
    df_print: paged
---
First we load all the libraries we will need to use.
```{r echo=FALSE, message=FALSE, error=FALSE, warning=FALSE, results='hide'}
include <- function(library_name){
  if( !(library_name %in% installed.packages()) )
    install.packages(library_name) 
  library(library_name, character.only=TRUE)
}
include("tidyverse")
include("knitr")
include("caret")
purl("insights.Rmd", output = "part1.r")
source("part1.r")
```

Now we will create a new column in the Person table that has every person's average rating that theyy gave songs.
```{r}
temp <- Ratings %>% group_by(psyeudonym) %>% summarise_at(vars(rating), funs(mean(.)))
colnames(temp)[colnames(temp)=="rating"] <- "avg_rating"
Person <- merge(Person, temp)
```

Now we will partition the data using random sampling into a training group and a testing group we will use later. The training group will have 75% of the data and will be what we use to create our model, then
the testing group will be used to see how well that model works.
```{r}
set.seed(123)
training.samples <- Person$avg_rating %>%
  createDataPartition(p = 0.75, list = FALSE)
train.data  <- Person[training.samples, ]
test.data <- Person[-training.samples, ]
```

Now we will test it on a few different variables:
```{r}
model <- lm(avg_rating ~ sex, data = train.data)
summary(model)
# Make predictions and compute the R2, RMSE and MAE
predictions <- model %>% predict(test.data)
data.frame( R2 = R2(predictions, test.data$avg_rating),
            RMSE = RMSE(predictions, test.data$avg_rating),
            MAE = MAE(predictions, test.data$avg_rating))
```


```{r}
model <- lm(avg_rating ~ academic_level, data = train.data)
summary(model)
# Make predictions and compute the R2, RMSE and MAE
predictions <- model %>% predict(test.data)
data.frame( R2 = R2(predictions, test.data$avg_rating),
            RMSE = RMSE(predictions, test.data$avg_rating),
            MAE = MAE(predictions, test.data$avg_rating))
```


```{r}
model <- lm(avg_rating ~ year_born, data = train.data)
summary(model)
# Make predictions and compute the R2, RMSE and MAE
predictions <- model %>% predict(test.data)
data.frame( R2 = R2(predictions, test.data$avg_rating),
            RMSE = RMSE(predictions, test.data$avg_rating),
            MAE = MAE(predictions, test.data$avg_rating))
```

Now we will create a model using multiple linear regression.
```{r}
model <- lm(data=train.data, formula=avg_rating~sex+academic_major+academic_level+year_born)
summary(model)
```
We can see that none of these variables are significant predictors.
